Plots

### 2023-04-11 Code/Plots.Rmd
ggplot boxplot

```{r}
set.seed(1)
library(lme4)
pdf(file = "Men_Density_Both.pdf")
fit2 <- glmer(RxnTime ~ (1 | Year) + (1 | Batch), data = men_pooled, family = Gamma(link = "log"))
fit0 <- glm(RxnTime ~ 1, data = men_pooled, family = Gamma(link = "log"))
sfit0 <- summary(fit0)
simfit <- function(fit2, n = 12000000) {
  vc <- as.data.frame(VarCorr(fit2))
  ## mu <- exp(coef(fit2)$Year[,]) ## using fitted random effects only
  z <- rnorm(n, sd = vc$sdcor[1]) #$ using generated random effects
  mu <- exp(fixef(fit2) + z)
  shape <- 1 / vc$vcov[2]
  x <- rgamma(n, shape = shape, scale = mu / shape)
  x
}

x <- simfit(fit2)
mean(x < 0.1)
quantile(x, prob = c(.00001, .0001, .0005, .001))
## compare with and without random effect
plot(density(x), main = "Men's Pooled With Year and Batch Effect") # with random effect
curve(dgamma(x, shape = 1 / sfit0$dispersion,
             scale = exp(coef(fit0)) * sfit0$dispersion),
      0.08, 0.22, add = TRUE, col = "orange") # fixed effect only
legend("right", title = "Probability mean less than", legend = " 0.1 is 0")
dev.off()
```
```{r}
set.seed(1)
library(lme4)
pdf(file = "Women_Density_Year.pdf")
fit2 <- glmer(RxnTime ~ (1 | Year), data = women_pooled, family = Gamma(link = "log"))
fit0 <- glm(RxnTime ~ 1, data = women_pooled, family = Gamma(link = "log"))
sfit0 <- summary(fit0)
simfit <- function(fit2, n = 12000000) {
  vc <- as.data.frame(VarCorr(fit2))
  ## mu <- exp(coef(fit2)$Year[,]) ## using fitted random effects only
  z <- rnorm(n, sd = vc$sdcor[1]) #$ using generated random effects
  mu <- exp(fixef(fit2) + z)
  shape <- 1 / vc$vcov[2]
  x <- rgamma(n, shape = shape, scale = mu / shape)
  x
}

x <- simfit(fit2)
mean(x < 0.1)
quantile(x, prob = c(.00001, .0001, .0005, .001))
## compare with and without random effect
plot(density(x), main = "Women's Pooled With Only Year Effect") # with random effect
curve(dgamma(x, shape = 1 / sfit0$dispersion,
             scale = exp(coef(fit0)) * sfit0$dispersion),
      0.08, 0.22, add = TRUE, col = "deeppink") # fixed effect only
legend("right", title = "Probability mean less than", legend = " 0.1 is 0.0042296")
dev.off()
```
```{r}
year_effect <- glmer(RxnTime ~ (1 | Year), data = men_pooled, family = Gamma(link = "log"))
batch_effect <- glmer(RxnTime ~ (1 | Batch), data = men_pooled, family = Gamma(link = "log"))
both <- glmer(RxnTime ~ (1 | Year) + (1 | Batch), data = men_pooled, family = Gamma(link = "log"))
#anova(batch_effect, both)
summary(both)
```

@@

```{r}
pdf(file = "BoxplotFinals.pdf")
boxplot(RxnTime ~ Year, data = men_finals, xlab = "Year", ylab = "Reaction Time in seconds", main = "Men's Final Reaction Time Boxplot Data")
dev.off()
```

>>>>

```{r}
set.seed(1)
library(lme4)
pdf(file = "Men_Density_Both.pdf")
fit2 <- glmer(RxnTime ~ (1 | Year) + (1 | Batch), data = men_pooled, family = Gamma(link = "log"))
fit0 <- glm(RxnTime ~ 1, data = men_pooled, family = Gamma(link = "log"))
sfit0 <- summary(fit0)
simfit <- function(fit2, n = 10000000) {
  vc <- as.data.frame(VarCorr(fit2))
  ## mu <- exp(coef(fit2)$Year[,]) ## using fitted random effects only
  z <- rnorm(n, sd = vc$sdcor[1]) #$ using generated random effects
  mu <- exp(fixef(fit2) + z)
  shape <- 1 / vc$vcov[2]
  x <- rgamma(n, shape = shape, scale = mu / shape)
  x
}

x <- simfit(fit2)
mean(x < 0.1)
quantile(x, prob = c(.00001, .0001, .0005, .001))
## compare with and without random effect
plot(density(x), main = "Men's Pooled With Year and Batch Effect") # with random effect
curve(dgamma(x, shape = 1 / sfit0$dispersion,
             scale = exp(coef(fit0)) * sfit0$dispersion),
      0.08, 0.22, add = TRUE, col = "orange") # fixed effect only
legend("right", title = "Probability mean less than", legend = " 0.1 is 0")
dev.off()
```

```{r}
set.seed(1)
library(lme4)
pdf(file = "Women_Density_Year.pdf")
fit2 <- glmer(RxnTime ~ (1 | Year), data = women_pooled, family = Gamma(link = "log"))
fit0 <- glm(RxnTime ~ 1, data = women_pooled, family = Gamma(link = "log"))
sfit0 <- summary(fit0)
simfit <- function(fit2, n = 10000000) {
  vc <- as.data.frame(VarCorr(fit2))
  ## mu <- exp(coef(fit2)$Year[,]) ## using fitted random effects only
  z <- rnorm(n, sd = vc$sdcor[1]) #$ using generated random effects
  mu <- exp(fixef(fit2) + z)
  shape <- 1 / vc$vcov[2]
  x <- rgamma(n, shape = shape, scale = mu / shape)
  x
}

x <- simfit(fit2)
mean(x < 0.1)
quantile(x, prob = c(.00001, .0001, .0005, .001))
## compare with and without random effect
plot(density(x), main = "Women's Pooled With Only Year Effect") # with random effect
curve(dgamma(x, shape = 1 / sfit0$dispersion,
             scale = exp(coef(fit0)) * sfit0$dispersion),
      0.08, 0.22, add = TRUE, col = "deeppink") # fixed effect only
legend("right", title = "Probability mean less than", legend = " 0.1 is 0.0042296")
dev.off()
```

```{r}
year_effect <- glmer(RxnTime ~ (1 | Year), data = men_pooled, family = Gamma(link = "log"))
batch_effect <- glmer(RxnTime ~ (1 | Batch), data = men_pooled, family = Gamma(link = "log"))
both <- glmer(RxnTime ~ (1 | Year) + (1 | Batch), data = men_pooled, family = Gamma(link = "log"))
#anova(batch_effect, both)
summary(both)
```

@@

```{r}
opar <- par()
par(mfrow = c(1,2))
pdf(file = "BoxplotFinals.pdf")
boxplot(RxnTime ~ Year, data = men_finals, xlab = "Year", ylab = "Reaction Time in seconds")
boxplot(RxnTime ~ Year, data = men_finals, xlab = "Year", ylab = "Reaction Time in seconds")
dev.off()
par(opar)
```

```{r}
#ggplot(data = win, aes(x = strength_diff)) + geom_boxplot() + theme_minimal()
ggplot(data = men_finals, aes(x=Year, y = RxnTime)) + geom_boxplot() + theme_minimal()
```

```{r}
library(gridExtra)
library(ggplot2)
final <- ggplot(men_finals, aes(x = Year, y = RxnTime, group = Year)) +
  geom_boxplot(fill = "lightblue", color = "darkblue") +
  labs(x = "Year", y = "Reaction Time (s)") +
       scale_y_continuous(limits = c(0.1, 0.225),
                            breaks = seq(0.1, 0.225, 0.025)) +
  expand_limits(y = 0.1) + scale_x_continuous(limits = c(1998,2023),
                                              breaks = seq(1997, 2022, 2))

pooled <- ggplot(men_pooled, aes(x = Year, y = RxnTime, group = Year)) +
  geom_boxplot(fill = "orange1", color = "orangered4") +
  labs(x = "Year", y = "Reaction Time (s)") +
       scale_y_continuous(limits = c(0.1, 0.225),
                            breaks = seq(0.1, 0.225, 0.025)) +
  expand_limits(y = 0.1) + scale_x_continuous(limits = c(1998,2023),
                                              breaks = seq(1997, 2022, 2))
both <- grid.arrange(final,pooled, ncol=1)
ggsave(filename="Finals_Pooled_Boxplot.pdf", path = "../Manuscript", plot=both, height = 6, width = 6)
```
